Motor Vehicle Collisions Reduced Across Toronto During and After the Beginning of the COVID-19 Pandemic

### 2024-01-23 outputs/paper/paper.qmd
Fixed grammar in discussion

According to @tbl-wardprofilestats and @sec-location, ward 1 and ward 21's population number is above the mean of 110452 people (also known as average) however both wards are below the mean of $46,436 in terms of average household income.

>>>>

According to @tbl-wardprofilestats and @sec-location, ward 1 and ward 21's population number are above the mean of 110452 people (also known as average) however both wards are below the mean of $46,436 in terms of average household income.
